---
title: "Exploration"
format: html
editor: visual
---

## Exploration of data

```{r}
library(tidyverse)
politicians <- read.csv("politicians_v3.csv", header = TRUE, stringsAsFactors = FALSE)
```

## All questions vs. all answers

This plot shows the questions-to-answer rate of all questions and answer from the elected politician from 17.07.2024 in Germany. About two thirds of the questions asked have been answered.

```{r}
answers <- sum(politicians$Q_answered)
questions <- sum(politicians$Q_asked)
data <- data.frame(
  "stats" = c(round((questions-answers)/questions*100, 2), round(answers/questions*100, 2)), 
  "category" = c("Unanswered", "Answered"))

ggplot(data = data, aes(x ="", y = stats, fill = category)) + 
  geom_col(color = "black") +
  geom_text(aes(label = paste0(stats, "%")), position = position_stack(vjust = 0.5))+
  coord_polar(theta = "y") +
  theme_void() +
  scale_fill_manual(values = c("#87BCDE", "#805E73")) +
  ggtitle(paste("Number of total questions:", questions))
```

## Questions and Answers in relation to their party

This code chunk will create a function, displaying a pie chart of given party. It takes the name of the party as string and color codes for the answered and unanswered questions as optional parameters.

```{r}
party_pie_chart <- function(party, color_a = "#87BCDE", color_u = "#805E73") {
  # filter data
  filtered_data <- filter(politicians, Party == party)
  print(filtered_data)
  answers <- sum(filtered_data$Q_answered)
  questions <- sum(filtered_data$Q_asked)
  
  # create data frame with data
  data <- data.frame(
    "stats" = c(round((questions-answers)/questions*100, 2), round(answers/questions*100, 2)), 
  "category" = c("Unanswered", "Answered"))
  
  # create pie chart
  ggplot(data = data, aes(x ="", y = stats, fill = category)) + 
  geom_col(color = "black") +
  geom_text(aes(label = paste0(stats, "%")), position = position_stack(vjust = 0.5))+
  coord_polar(theta = "y") +
  theme_void() +
  scale_fill_manual(values = c(color_a, color_u)) +
  ggtitle(paste("Total questions:", questions, "- Party:", party))
}
```

This plot shows the answered-unanswered-question-ratio of the CDU. The CDU has been asked 4410 questions and 35% of the questions have not been answered.

```{r}
party_pie_chart(" CDU")
```

This plot shows the answered-unanswered-question-ratio of the CDU. The CDU has been asked 814 questions and 23% of the questions have not been answered

```{r}
party_pie_chart(" CSU")
```

This plot shows the answered-unanswered-question-ratio of the FDP. The FDP has been asked 6019 questions and 27% have not been answered.

```{r}
party_pie_chart(" FDP")
```

This plot shows the answered-unanswered-question-ratio of the SPD. The SPD has been asked 11970 questions and 19% have not been answered.

```{r}
party_pie_chart(" SPD")
```

This plot shows the answered-unanswered-question-ratio of the Bündnis 90/Die Grünen. The Bündnis 90/Die Grünen has been asked 9495 questions and 28% have not been answered.

```{r}
party_pie_chart(" Bündnis 90/Die Grünen")
```

This plot shows the answered-unanswered-question-ratio of the AfD. The AfD has been asked 2038 questions and 24% have not been answered.

```{r}
party_pie_chart(" AfD")
```

This plot shows the answered-unanswered-question-ratio of the DIE LINKE. The DIE LINKE has been asked 1704 questions and 12% have not been answered.

```{r}
party_pie_chart(" DIE LINKE")
```
